\bf Range Analysis for the IonMonkey JavaScript Compiler

### 2012-05-02 project-writings/paper.tex
fix wording about range analysis correctness
minor nits, done

\title{\bf Range Analysis for the IonMonkey JavaScript engine}

@@

\subsection{Conditional Branches and $\beta$ nobes}

@@

Thus we developed a quite simple and in practice efficient algorithm to
add $\beta$ nodes to an SSA source program by taking
advantage of data structures common to modern SSA based compilers
\footnote{The method for removing $\beta$ nodes is so trivial that we
  could not claim with a straight face that we ``developed an
  algorithm'' to perform it.} .  Pseudocode for the algorithm is shown
in Listing \ref{lst:add_betas}. The algorithm traverses the control
flow group, looking for blocks that have been entered by a jump
conditioned on a relational operation. When we find a variable being
compared to a constant, we compute a range and use it to create a new
$\beta$ node. As a further optimization, we furthermore insert trivial beta
nodes when we encounter a
strict comparison between two variables--the larger must be at least
$-2^{31}+1$, and the smaller can be at most $2^{31}-2$.

@@

Our algorithm for range analsis is based on the algorithm due to Gough. It
differs from the paper in a few ways to better fit the architecture of
IonMonkey. The paper suggests using a dominator tree order, but we found that
using reverse post-order was better for our purposes: reverse post-order
traversal is simpler to implement in IonMonkey, and in general definitions are
still visited before all their uses. There is no issue of correctness since we
iterate until no range information is changing.

>>>>

\title{\bf Range Analysis for the IonMonkey JavaScript Compiler}

@@

\subsection{Conditional Branches and $\beta$ Nodes}

@@

Thus we developed a quite simple and in practice efficient algorithm to
add $\beta$ nodes to an SSA source program by taking
advantage of data structures common to modern SSA based compilers
\footnote{The method for removing $\beta$ nodes is so trivial that we
  could not claim with a straight face that we ``developed an
  algorithm'' to perform it.} .  Pseudocode for the algorithm is shown
in Listing \ref{lst:add_betas}. The algorithm traverses the control
flow group, looking for blocks that have been entered by a jump
conditioned on a relational operation. When we find a variable being
compared to a constant, we compute a range and use it to create a new
$\beta$ node. As an additional optimization, we furthermore insert trivial beta
nodes when we encounter a
strict comparison between two variables--the larger must be at least
$-2^{31}+1$, and the smaller can be at most $2^{31}-2$.

@@

Our algorithm for range analsis is based on the algorithm due to Gough. It
differs from the paper in a few ways to better fit the architecture of
IonMonkey. The paper suggests using a dominator tree order, but we found that
using reverse post-order was better for our purposes: reverse post-order
traversal is simpler to implement in IonMonkey, and in general definitions are
still visited before all their uses. There is no issue of correctness since at
all points in the algorithm, the range information holds.
